---
title: "Lab Assessment-1"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Register Number: 18BCE1065
### Name: Siddharth Singha Roy
### Dataset Name: Parkinson Disease Spiral Drawings

### Design any 10 questions for data manipulation

* * *
Question-1 : Read the data and display all information about the dataset

```{r}
#Type your code here
library(knitr)
library(dplyr)
library(data.table)
library(stringr)
library(lubridate)
library(tidyr)
library(ggplot2)
data = fread("/home/siddharth/Downloads/parkinsons.data")
head(data)
colnames(data)
dim(data)
```

* * *
Question-2 : Rename column name to Name, status to Status, spread1 to Spread1 and spread2 to Spread2

```{r}
#Type your code here
colnames(data)[1] = "Name"
colnames(data)[21] = "Spread1"
colnames(data)[22] = "Spread2"
colnames(data)[18] = "Status"
colnames(data)
```

* * *
Question-3 : Get all name where status = 0

```{r}
#Type your code here
filter(data, Status == 0)
```

* * *
Question-4 : Find number of missing data for each column

```{r}
#Type your code here
for(i in colnames(data)) {
  print(paste("Column :", i, "Missing Values :", sum(is.na(data[, ..i])), sep=" "))
}
```
* * *
Question-5 : Compute the correlation score

```{r}
#Type your code here
data = data[, .SD, .SDcols = which(sapply(data, is.numeric))]
cor(data, use = "na.or.complete")
```

* * *
Question-6 : Remove column D2

```{r}
#Type your code here
data = select(data, -"D2")
colnames(data)
```

* * *
Question-7 : Shuffle the rows

```{r}
#Type your code here
set.seed(1000)
data[sample(nrow(data), replace = T),]
head(data)
```

* * *
Question-8 : Convert negative spread1 to positive

```{r}
#Type your code here
data$Spread1 = abs(data$Spread1)
data$Spread1
```

* * *
Question-9 : Order dataset by PPE Ascending

```{r}
#Type your code here
data[,][order(PPE)]
```
* * *
Question-10 : Select all numeric columns and summarize its information

```{r}
#Type your code here
summary(select(data, where(is.numeric)))
```

### Design any 5 Elementary Statistical questions for the given dataset

* * *
Question-1 : Create a contingency table for Status

```{r}
#Type your code here
xtabs(~Status, data=data)
```

* * *
Question-2 : Summarize all the data

```{r}
#Type your code here
summary(data)
```

* * *
Question-3 : 

```{r}
#Type your code here
```

* * *
Question-4 here

```{r}
#Type your code here
```
* * *
Question-5 here

```{r}
#Type your code here
```

### Design any 5 appropriate questions for data exploration
* * *
Question-1 : Boxplot for Status

```{r}
#Type your code here
box<-ggplot(data,mapping=aes(x=Status,y=NHR, group=Status))+geom_boxplot()
plot(box)

# The above box plot shows some outliers for NHR when Status=1
```

* * *
Question-2 : Histogram for NHR


```{r}
#Type your code here
hist<-ggplot(data,aes(x=NHR))+geom_histogram(color="pink",fill="green")
plot(hist)

# So the column NHR is right skewed
```

* * *
Question-3 : Jitter plot for Status and PPE

```{r}
#Type your code here
jitter<-ggplot(data,aes(PPE,Status))+geom_point()+geom_jitter()
plot(jitter)
```

* * *
Question-4 : Histogram for PPE


```{r}
#Type your code here
hist2<-ggplot(data,aes(x=PPE))+geom_histogram(color="pink",fill="green")
plot(hist2)

# The column contains a double hump and is well distributed over the mean
```
* * *
Question-5 : Analyse Spread1 and Spread2 via count chart

```{r}
#Type your code here
count_chart <- ggplot(data, aes(x=Spread1, y=Spread2)) +
  geom_count(col="blue", show.legend=F)
plot(count_chart)

# Shows the value for which Spread1 and Spread2 become highly concentrated
```